---
title: "game_sales_analysis"
output: html_notebook
---

# Load packages

```{r}
#devtools::install_github("hrbrmstr/waffle")

# Data wrangling
library(tidyverse)
library(janitor)
# Data loading/saving
library(readxl)
# Fro currency
library(formattable)
#for cahrts
library(waffle)
library(hrbrthemes)
library(ggpubr)
library(plotly)
library(ggiraph)
library(corrgram)
```

# Load file

```{r}
raw_game_data <- readxl::read_xlsx("raw_data/Recrutiment task - data set.xlsx")

glimpse(raw_game_data)
```

# Check if data set contains any NA
1. Data set is "full".
2. From glimpse: We got some categorical variables all of the are nominal (or if it comes to games industry we could make some order in platform)


```{r}
colSums(is.na(raw_game_data))
```

#Data cleaning
1. Clean col names with janitor (make em more "R way")
2. Show number of unique values in every column
3. Remove columns containing only 1 value. Create factor columns for further analysis.
4. Create Map table with country code and country name.
5. Create a column that shows if game is promoted (near is better than "==" cos of floats.). Add % of discount in-country curr
6. Split data set by years 

```{r}
data_clean_names <- janitor::clean_names(raw_game_data)

number_of_unique_values_in_col <- data_clean_names %>% 
  summarise_all(n_distinct) %>%
  pivot_longer(cols = everything(),
               names_to = "n_distinct")

data_column_choice <- data_clean_names %>%
  select(- package, -product_name, -type, -product_id_number) %>%
  mutate_if(~(is_character(.) & n_distinct(.) <= 130), as.factor)

country_map_table <- data_column_choice %>%
  select(country_code, country)
                
game_is_promo <- data_column_choice %>%
  select(-country) %>%
  mutate(
    unit_net_price_usd = net_sales_usd/net_units_sold,
    is_promo = !(near(base_price, sale_price)),
    promo_rev = ifelse(is_promo == T, net_sales_usd,0),
    normal_rev = ifelse(is_promo == F, net_sales_usd,0),
    discount = ifelse(is_promo, round((1-(sale_price/base_price))*100),0),
    sales_season = as.factor(ifelse(date < '2017-02-02',1,2)),
    winter_sales = as.factor(ifelse(date > '2016-12-22' & date < '2017-01-03',
                                    "ws1",
                                    ifelse(date > '2017-12-21' & date < '2018-01-04',
                                           "ws2",
                                           "no_ws")))
  ) %>%
  arrange(country_code)

first_sales <- game_is_promo %>%
  filter(date < '2017-02-02')

second_sales <- game_is_promo %>%
  filter(date > '2017-02-02')

game_is_promo %>%
  summarise_all(how_many_na)
```

# Quick summary after cleaning

```{r}
game_is_promo %>% 
    select_if(is.numeric) %>%
    summary()
```

# Grouping data
1. Group data by platform
2. Create additional groups for discount - dropped in the process - useless conception. 

```{r}
options(scipen = 999)

discount_by_platform <- first_sales %>%
  group_by(platform, discount) %>%
  summarise(numb = n(), sum_net = sum(net_sales_usd)) %>%
  mutate(perc_group = numb/sum(numb), sum_net_group_perc = sum_net/sum(sum_net)) %>%
  ungroup() %>%
  mutate(perc_ungroup = numb/sum(numb), sum_net_ungroup = sum_net/sum(sum_net))

discount_by_platform_whole_data <- count_occurencies(game_is_promo, platform, discount)

discount_new_group <- game_is_promo %>%
  mutate(new_groups = case_when(
    discount == 0 ~ "0",
    discount > 0 & discount < 30 ~ "29-",
    discount >= 30 & discount < 40 ~ "30~39",
    discount >= 40 & discount < 50 ~ "40-49",
    discount >= 50 & discount < 59 ~ "50~59",
    discount >= 60 ~ "60+")
   )
```

# Check discount in winter sales
1. Filter data
2. Use custom function for proper grouping and count.
3. Check unusual discount 

```{r}
sales_period <- game_is_promo %>%
  filter(winter_sales != "no_ws", is_promo == T)

count_occurencies(sales_period, winter_sales, discount) %>%
  group_by(winter_sales) %>%
  top_n(1, wt = numb) %>%
  select(winter_sales, discount) %>%
  rename(Discount = discount, "Sales Season" = winter_sales)

check_disc_42 <- sales_period %>%
  filter(winter_sales == "ws1", discount == 42)


#During WS1 discount was at 32% 
#During WS2 discount was at 40%.
```

# Check by region

```{r}

test_price <- sales_period %>%
  filter(!is.nan(unit_net_price_usd )) %>%
  group_by(region) %>%
  summarise(mean_price = mean(unit_net_price_usd))


```

# Custom themes
1. theme for waffle chart.
2. The theme for simple line plot that will be converted to plotly objects. 

```{r}
waffle_theme_custom <- theme(
     plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
     plot.subtitle = element_text(hjust = 0.5, size = 10, face = "italic"),
     panel.background = element_rect(fill = "transparent", colour = NA),
     legend.text = element_text(hjust = 0.5, size = 9),
     legend.title = element_blank(),
     legend.key = element_rect(size = 5),
     legend.position = "bottom",
     legend.justification = "center",
     legend.margin = margin(0, 0, 0, 0),
     legend.spacing.x = unit(0, "pt"),
     plot.caption = element_text(hjust = 1, face = "italic"),
     axis.ticks = element_blank(),
     axis.title = element_blank(),
     axis.text = element_blank(),
     plot.margin=unit(c(1,1,1,1), "lines", )
   )

simple_line_theme <- theme(
     plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
     plot.subtitle = element_text(hjust = 0.5, size = 10, face = "italic"),
     axis.text.x = element_text(angle = 90, hjust = 1, size = 8, face = "bold"),
     axis.text.y = element_text(face ="italic"),
     legend.text = element_text(hjust = 0.5, size = 9),
     legend.position = c(0.8, 0.2),
     legend.title = element_blank(),
     legend.justification = "center",
     axis.title = element_text(hjust = 0.5, size = 10, face = "bold"),
     panel.background = element_rect(fill = "transparent", colour = NA),
     plot.margin=unit(c(1,1,1,1), "lines"),
     plot.caption = element_text(hjust = 1, face = "italic"),
   )

simple_bar_theme <- theme(
     plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
     plot.subtitle = element_text(hjust = 0.5, size = 10, face = "italic"),
     axis.text.x = element_text(angle = 90, hjust = 1, size = 8, face = "bold"),
     axis.text.y = element_text(face ="italic"),
     legend.text = element_text(hjust = 0.5, size = 9),
     legend.title = element_blank(),
     legend.justification = "center",
     axis.title = element_text(hjust = 0.5, size = 10, face = "bold"),
     panel.background = element_rect(fill = "transparent", colour = NA),
     plot.margin=unit(c(1,1,1,1), "lines"),
     plot.caption = element_text(hjust = 1, face = "italic"),
   )
```

#Draw line plots:
1. Create proper data set for plotting.
2. Create one test plot, then convert it to function.
3. Use function with different parameters.  

```{r}
date_group <- game_is_promo %>%
  group_by(date) %>%
  summarise(numb = n(), sum_revenu = sum(net_sales_usd), sum_net_sales = sum(net_units_sold), 
            sum_ret = sum(returns), mean_reve = mean(net_sales_usd), sum_promo_rev = sum(promo_rev), 
            sum_norm_rev = sum(normal_rev), ret_to_sell = sum_ret/sum_net_sales, unit_net_rev = sum_revenu/sum_net_sales) %>%
  mutate(sales_season = as.factor(ifelse(date < '2017-02-02',1,2)),
         day_month = format(date, "%m-%d")) %>%
  arrange(date) %>%
  mutate(id = row_number()) %>%
  ungroup() %>%
  mutate(day_month = fct_reorder(day_month,id),
         winter_sales = as.factor(ifelse(date > '2016-12-22' & date < '2017-01-03',
                                    "ws1",
                                    ifelse(date > '2017-12-21' & date < '2018-01-04',
                                           "ws2",
                                           "no_ws"))))

total_revenu <- ggplot(date_group, aes(x = day_month, y = sum_revenu, group = sales_season, colour = sales_season)) +
  geom_line() +
  geom_point() +
  labs(title="Netto sales revenue in USD divided by seasons",
       x = "Day and Month of sales",
       y = "Netto revenue") +
  simple_line_theme

plotly_ojb <- ggplotly(t) 

plotly_ojb %>% 
  layout(legend = list(title=list(text='<b> Sales Season </b>')))

basic_line_season(sum_norm_rev)
basic_line_season(sum_net_sales)
basic_line_season(sum_ret)
basic_line_season(ret_to_sell)
basic_line_season(unit_net_rev)
```

# Some tests
1. We'll chech if sales distribution (number of net sales) are identical in both seasons (2 months period)
- H0: Populations are the same in both seasons. p-value = 0.75 so we can't reject the null hypothesis
2. Create data sets for further tests.
3. We'll check if netto revenue distribution (sum of netto revenue) are identical in both sales. 
4. Check some density and box plots. 

```{r}
#test whole period.H0: NOT rejected
wilcox.test(sum_net_sales ~ sales_season, data=date_group)

only_ws_data <- date_group %>%
  filter(winter_sales != "no_ws") %>%
  group_by(winter_sales) %>%
  mutate(rev_promo_rate = round(sum_promo_rev/lag(sum_promo_rev) * 100,2)) %>%
  ungroup()

mean_price <- only_ws_data %>%
  group_by(winter_sales) %>%
  summarise(mean_unit = round(mean(unit_net_rev),2)) %>%
  ungroup() %>%
  mutate(discount = c(0.32,0.4),
         norm_price = round((mean_unit/(1-discount)),2))

only_no_ws_data <- date_group %>%
  filter(winter_sales == "no_ws") %>%
  group_by(sales_season) %>%
  mutate(rev_growth_rate = round(sum_norm_rev/lag(sum_norm_rev) * 100,2)) %>%
  ungroup()
  


#Check distribution of revenues in both sales period. H0: rejected.
wilcox.test(sum_promo_rev ~ winter_sales, data=only_ws_data)
#Check distribution of rates of revenues in both sales period. H0: NOT rejected
wilcox.test(rev_promo_rate ~ winter_sales, data=only_ws_data)

#Check distribution of revenues in no sales period. H0: NOT rejected
wilcox.test(sum_norm_rev ~ sales_season, data=only_no_ws_data)


ggplot(only_ws_data, aes(x = rev_promo_rate)) +
  geom_histogram(bins = 6) +
  facet_grid(~ winter_sales)

ggplot(date_group, aes(x = sum_net_sales, group = sales_season)) +
  geom_boxplot()

ggplot(only_ws_data, aes(x = rev_promo_rate, color = winter_sales)) +
  geom_density()

ggplot(only_no_ws_data, aes(x = sum_norm_rev, color = sales_season)) +
  geom_density()

ggplot(only_no_ws_data, aes(x = sum_norm_rev)) +
  geom_histogram(bins = 8) +
  facet_grid(~ sales_season)

basic_line_season(rev_promo_rate, data = only_ws_data, "Plot 2. Netto Revenue from products on promotion in USD", "Netto revenue in USD")
```

# Create Pie charts.

```{r}
test_pie <- ggplot(plat_numb_trans_whole, aes(x="", y=perc_group, fill=platform)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) + 
  theme_void() + 
  scale_fill_brewer(palette="Set1")


data_pie_chart_s1 <- date_group %>%
  filter(sales_season == 1)
  
data_pie_chart_s2 <- date_group %>%
  filter(sales_season == 2)
  
fig <- plot_ly()

fig <- fig %>% add_pie(data = data_pie_chart_s1, labels = ~winter_sales, values = ~sum_revenu, name = "S1", domain = list(row = 0, column = 0))
fig <- fig %>% add_pie(data = data_pie_chart_s2, labels = ~winter_sales, values = ~sum_revenu, name = "S2", domain = list(row = 0, column = 1))

fig <- fig %>% layout(title = "", showlegend = T,
                      grid=list(rows=1, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig
```

# Create table 

```{r}
count_param(date_group, sum_net_sales, sales_season, winter_sales) %>%
  mutate(count_sum_group = percent(count_sum_group),
         count_sum_ungroup = percent(count_sum_ungroup)) %>%
  rename("Sales Season" = sales_season, "Winter Sales" = winter_sales, Duration = numb, "Copies Sold" = sum_net, 
         "Perc inside group" = count_sum_group, "Perc without gruping" = count_sum_ungroup)
```

# region analysis
1. Prepare the data
2. Draw bar plot. 

```{r}
region_revenue <- game_is_promo %>%
  group_by(sales_season, winter_sales, region) %>%
  summarise(sum_rev = sum(net_sales_usd)) %>%
  mutate(rev_group_perc = sum_rev/sum(sum_rev)) %>%
  ungroup() %>%
  mutate(rev_group_perc = percent(rev_group_perc)) %>%
  mutate(rev_ungroup_perc = percent(sum_rev/sum(sum_rev))) %>%
  arrange(sales_season, winter_sales, desc(rev_group_perc))
  
region_sales <- game_is_promo %>%
  group_by(sales_season, winter_sales, region) %>%
  summarise(sum_net_sales = sum(net_units_sold)) %>%
  mutate(copy_sales_group_perc = sum_net_sales/sum(sum_net_sales)) %>%
  ungroup() %>%
  mutate(copy_sales_group_perc = percent(copy_sales_group_perc)) %>%
  mutate(copy_sales_ungroup_perc = percent(sum_net_sales/sum(sum_net_sales))) %>%
  arrange(sales_season, winter_sales, desc(copy_sales_group_perc))

region_rev_whole_year <- region_revenue %>%
  group_by(region, sales_season) %>%
  summarise(sum_rev = sum(sum_rev), perc = sum(rev_ungroup_perc))
 
 

draw_simple_bar <- function(data, y_val, title = "add title", ylab_title = "add_y_lab_name") {
  simple_bar <- ggplot(data, aes(x = reorder(region, -{{y_val}}), y = {{y_val}})) +
    geom_bar(stat="identity") +
    labs(title=title,
         x = "Regions",
         y = ylab_title) +
    simple_bar_theme 
  
  ret_obj <- ggplotly(simple_bar)
  return(ret_obj)
}

draw_simple_bar(region_rev_whole_year, perc)
```

# Draw waffle chart for raport. 

```{r}
plat_numb_trans_whole <- count_occurencies(game_is_promo, platform) %>%
  mutate(ypos = cumsum(perc_group) - perc_group/25,
         perc_chart = percent(perc_group),
         waffle_chart = round(perc_group*100))

plat_numb_trans_s1 <- create_waffle_count(first_sales, count_occurencies, platform)
plat_numb_trans_s2 <- create_waffle_count(second_sales, count_occurencies, platform)

plat_sales_whole <- create_waffle_param(game_is_promo, count_param, net_sales_usd, platform)
plat_sales_s1 <- create_waffle_param(first_sales, count_param, net_sales_usd, platform)
plat_sales_s2 <- create_waffle_param(second_sales, count_param, net_sales_usd, platform)

plat_net_num_whole <- create_waffle_param(game_is_promo, count_param, net_units_sold, platform)
plat_net_num_s1 <- create_waffle_param(first_sales, count_param, net_units_sold, platform)
plat_net_num_s2 <- create_waffle_param(second_sales, count_param,net_units_sold, platform)

both_promo_waffle <- ggplot(plat_numb_trans_whole, aes(fill = platform, values = waffle_chart)) +
  geom_waffle(n_rows = 10, size = 0.33, colour = "white", flip = TRUE) +
  labs(subtitle="transactions made in both sales") +
  coord_equal() +
  theme_enhance_waffle() +
  waffle_theme_custom

first_promo_waffle <- create_waffle_chart(plat_numb_trans_s1, platform, waffle_chart, 
                                          "transactions made in sales 1")

second_promo_waffle <- create_waffle_chart(plat_numb_trans_s2, platform, waffle_chart, 
                                          "transactions made in sales 2")

both_promo_waffle_sales <- create_waffle_chart(plat_sales_whole, platform, waffle_chart,
                                               "Revenue in both sales")

first_promo_waffle_sales <- create_waffle_chart(plat_sales_s1, platform, waffle_chart,
                                               "Revenue in S1")

second_promo_waffle_sales <- create_waffle_chart(plat_sales_s2, platform, waffle_chart,
                                               "Revenue in S2")

both_promo_waffle_numb <- create_waffle_chart(plat_net_num_whole, platform, waffle_chart,
                                               "Copies sold in both sales")

first_promo_waffle_numb <- create_waffle_chart(plat_net_num_s1, platform, waffle_chart,
                                               "Copies sold in S1")

second_promo_waffle_numb <- create_waffle_chart(plat_net_num_s2, platform, waffle_chart,
                                               "Copies sold in S2")

arrange_trans <- ggarrange(both_promo_waffle, first_promo_waffle, second_promo_waffle, 
                           legend = "none", ncol = 3)

arrange_sold_copies <- ggarrange(both_promo_waffle_numb, first_promo_waffle_numb, second_promo_waffle_numb, 
                                 legend = "none",  ncol = 3)

arrange_revenues <- ggarrange(both_promo_waffle_sales, first_promo_waffle_sales, second_promo_waffle_sales, 
                              common.legend = TRUE, legend = "bottom", ncol = 3)

ann_trans <- annotate_figure(p = arrange_trans, top = text_grob("Waffle charts in percentage divided by platform", face = "bold", size = 14))

ann_revenues <- annotate_figure(p = arrange_revenues,bottom = text_grob("1 square == 1pp", color = "blue", hjust = 1, x = 1, face = "italic", size = 8))



ann_trans
arrange_sold_copies
ann_revenues
```

# 

```{r}

# game_is_promo %>%
#   group_by(sales_season, winter_sales, platform) %>%
#   summarise(numb = n(), sum_rev = sum(net_sales_usd), sum_net_sales = sum(net_units_sold)) %>%
#   mutate(rev_group_perc = sum_rev/sum(sum_rev), copy_sales_group_perc = sum_net_sales/sum(sum_net_sales)) %>%
#   ungroup() %>%
#   mutate(rev_group_perc = percent(rev_group_perc), copy_sales_group_perc = percent(copy_sales_group_perc)) %>%
# summarise(numb = n(), sum_revenu = sum(net_sales_usd), sum_net_sales = sum(net_units_sold), 
#             sum_ret = sum(returns), mean_reve = mean(net_sales_usd), sum_promo_rev = sum(promo_rev), 
#             sum_norm_rev = sum(normal_rev), ret_to_sell = sum_ret/sum_net_sales, unit_net_rev = sum_revenu/sum_net_sales) %>%
#   mutate(sales_season = as.factor(ifelse(date < '2017-02-02',1,2)),
#          day_month = format(date, "%m-%d")) %>%
#   arrange(date) %>%
#   mutate(id = row_number()) %>%
#   ungroup() %>%
#   mutate(day_month = fct_reorder(day_month,id),
#          winter_sales = as.factor(ifelse(date > '2016-12-22' & date < '2017-01-03',
#                                     "ws1",
#                                     ifelse(date > '2017-12-21' & date < '2018-01-04',
#                                            "ws2",
#                                            "no_ws"))))

```

# Functions
1. 

```{r}
count_occurencies <- function(data, ...) {
  result <-data %>%
    group_by(...) %>%
    summarise(numb = n()) %>%
    mutate(perc_group = numb/sum(numb)) %>%
    ungroup() %>%
    mutate(perc_ungroup = numb/sum(numb))
  return(result)
}

count_param <- function(data, col_to_sum, ...) {
  col_name <- enquo(col_to_sum)
  result <- data %>%
    group_by(...) %>%
    summarise(numb = n(), sum_net = sum(!!col_name)) %>%
    mutate(count_sum_group = sum_net/sum(sum_net)) %>%
    ungroup() %>%
    mutate(count_sum_ungroup = sum_net/sum(sum_net))
  return(result)
}

create_waffle_chart <- function(data, fill, values, subtitle) {
  ggplot(data, aes(fill = {{fill}}, values = {{values}})) +
  geom_waffle(n_rows = 10, size = 0.33, colour = "white", flip = TRUE) +
  labs(subtitle=subtitle) +
  coord_equal() +
  theme_enhance_waffle() +
  waffle_theme_custom
}

create_waffle_count <- function(data, fun_name, ...) {
  fun_name(data, ...) %>%
  mutate(perc_chart = percent(perc_group),
         waffle_chart = round(perc_group*100))
}

create_waffle_param <- function(data, fun_name, ...) {
  fun_name(data, ...) %>%
  mutate(perc_chart = percent(count_sum_group),
         waffle_chart = round(count_sum_group*100))
}

basic_line_season <- function (y_val, data = "date_group", title ="add title", ylab_title = "name_lab") {
ggplot_obj <- ggplot(data, aes(x = day_month, y = {{y_val}}, group = sales_season, colour = sales_season)) +
  geom_line() +
  geom_point() +
  labs(title=title,
       x = "Day and Month of sales",
       y = ylab_title) +
  simple_line_theme

plotly_ojb <- ggplotly(ggplot_obj) 

ret_obj <- plotly_ojb %>% 
  layout(legend = list(title=list(text='<b>Sales Season:</b>')))

return(ret_obj)
}
```

# Unused plots:
1. Pie chart - looking bad, many troubles, and way less informative than waffle chart 

```{r}
ggplot(plat_numb_trans_whole, aes(x="", y=perc_group, fill=platform)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) + 
  theme_void() + 
  scale_fill_brewer(palette="Set1")
```

# Add currency data (unused - bad concept)

```{r}
test <- game_is_promo %>%
  filter(net_units_sold >= 0, net_units_sold <= 1, currency %in% c("EUR","USD")) %>%
  mutate(
         unit_usd = if_else(near(net_sales_usd,0), gross_sales_usd/gross_units_sold, net_sales_usd/net_units_sold),
         test = near(unit_usd, sale_price),
         usd_course = sale_price/unit_usd
         ) %>%
  select(-platform)
  arrange(currency)
  
test_sample <- sample_n(game_is_promo, 500)


test_sample <- test_sample %>%
  arrange(currency) %>%
  mutate(
    net_sales_curr = sale_price*net_units_sold,
    one_usd_curr = net_sales_curr/net_sales_usd
  )

test_ret_zero <- test_sample %>%
  filter(!(near(returns_usd,0))) %>%
  mutate(
    vat_tax_usd = currency(vat_tax_usd),
    net_sales_usd = currency(net_sales_usd),
    returns_usd = currency(returns_usd),
    gross_sales_usd = currency(gross_sales_usd),
    stawka = round(as.numeric(-vat_tax_usd/net_sales_usd),2),
    gross_sales_curr = round((sale_price*net_units_sold)*(1+stawka),2)
         ) %>%
  arrange(country_code,date)

```



